Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2023-01-08 paper/introduction.tex
implement Nikos's suggestion to rephrase sentence in introduction section

In our work, we set out to produce a fast TBR surrogate model, which takes the same input parameters as the MC model used in Paramak and approximates its output with the greatest achievable regression performance, while also minimising the required quantity of expensive-model samples needed for training. This represents a significant step forwards in computational fusion-reactor design, as any speed-up achieved in TBR evaluation directly informs a speed-up in numerical optimization of reactor parameters, although such optimization is beyond the scope of the present work.

>>>>

In our work, we set out to produce a fast TBR surrogate model, which takes the
same input parameters as the MC model used in Paramak and approximates its
output with the greatest achievable regression performance, while also
minimising the required quantity of expensive-model samples needed for training.
This represents a significant step forward in computational fusion-reactor
design, as speed-ups achieved in TBR evaluation can lead to a speed-up in
numerical optimization of reactor parameters, although such optimization is
beyond the scope of the present work.
